A Review of Lossless Data Compression Methods

### 2018-11-19 paper.tex
Let's just say this is an ok first draft. probably has problems.

\title{A Review of Lossless Data Compression Methods}
\author{someone idk}

@@

In the age of ever-expanding quantities of digital data, the ability
to store this data efficiently is more important than ever. Throughout
the history of the field of computer science, various algorithms of
varying complexities and efficacies have been created in order to
reduce the amount of space required to store arbitrary strings of
binary data. This wide variety of methods are optimized for different
purposes: some algorithms attempt to reduce the amount of space
required to store raster images; some try to optimize audio storage;
some can optimize genetic data to an extremely high degree; and still
more attempt to work well for general-purpose use. Within the scope of
this paper, I will attempt to give an overview of a handful of popular
compression schemes, including general purpose in addition to
domain-specific methods, as well as a theoretical overview of the
limits and potential benefits of compression in general. This paper
will only cover lossless data encoding: that is, alogrithms which can
reproduce a perfect copy of the input data from its output. Lossy
compression schemes exist which can achieve incredible compression
ratios, but their methods typically include psychological ``tricks''
which allows the algorithm to discard data which is less noticable to
human senses. As such, these methods are outside the scope of this
paper.

@@

@@

>>>>

\title{A Review of Lossless Data Compression Methods}
\author{5251 Student}

@@

In the age of ever-expanding quantities of digital data, the ability
to store this data efficiently is more important than ever. Throughout
the history of the field of computer science, algorithms of varying
complexities and efficacies have been created in order to reduce the
amount of space required to store arbitrary strings of binary
data. This wide variety of methods are optimized for different
purposes: some algorithms attempt to reduce the amount of space
required to store raster images; some try to optimize audio storage;
some can optimize genetic data to an extremely high degree; and still
more attempt to work well for general-purpose use. Within the scope of
this paper, I will attempt to give an overview of a handful of popular
compression schemes, including general purpose in addition to
domain-specific methods, as well as a theoretical overview of the
limits and potential benefits of compression in general. This paper
will only cover lossless data encoding: that is, alogrithms which can
reproduce a perfect copy of the input data from its output. Lossy
compression schemes exist which can achieve incredible compression
ratios, but their methods typically include psychological ``tricks''
which allows the algorithm to discard data which is less noticable to
human senses. As such, these methods are outside the scope of this
paper.

@@

The FLAC specification is of course much more detailed than this
high-level overview, but a brief description of FLAC's methods is more
than sufficient to demonstrate how exploiting characteristics of a
particular data domain can lead to huge increases in compression
efficiency.

@@

Data compression methods can be used to reduce the amount of space
required to store digital data. However, tradeoffs have to be made
when compressing since it is impossible for an algorithm to be able to
compress any arbitrary input; some input must result in an output of
equal length. In addition, the compressability of an input is highly
dependent on its entropy. Many different compression algorithms exist,
the most common of which belong to the Lempel-Ziv family. Finally,
many domain-specific algorithms exist to gain extra efficiency when
applied to their particular domain. FLAC is one such algorithm which
is used for lossless audio storage and transmission.
